maze-dataset: Maze Generation with Algorithmic Variety and Representational Flexibility

### 2025-05-28 docs/paper/paper.tex
fix some figures, cut some sections

\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\urlstyle{same}  % don't use monospace font for urls
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{american}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{\textbf{#1}}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}

\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc}
\tikzset{ % Define a TikZ style for an external hyperlink node.
  hyperlink node url/.style={
    alias=sourcenode,
    append after command={
      let \p1 = (sourcenode.north west),
          \p2 = (sourcenode.south east),
          \n1 = {\x2-\x1},
          \n2 = {\y1-\y2} in
      node[inner sep=0pt, outer sep=0pt, anchor=north west, at=(\p1)]
          {\href{#1}{\XeTeXLinkBox{\phantom{\rule{\n1}{\n2}}}}}
    }
  }
}
\providecommand{\XeTeXLinkBox}[1]{#1}
\newcommand{\docslink}[2]{\href{https://understanding-search.github.io/maze-dataset/#1}{#2}}
\newcommand{\docslinkcode}[2]{\href{https://understanding-search.github.io/maze-dataset/#1}{\texttt{#2}}}
\newcommand{\docslinkcodemain}[1]{\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\##1}{\texttt{#1}}}
\newcommand{\secref}[1]{\hyperref[#1]{section: \textit{\nameref{#1}}}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

  \begin{itemize}
  \tightlist
  \item
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/rasterized.html\#RasterizedMazeDataset}{\texttt{RasterizedMazeDataset}},
    utilizing
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze.as_pixels}{\texttt{as\_pixels()}},
    which can exactly mimic the outputs provided in
    \texttt{easy-to-hard-data}(\protect\hyperlink{ref-easy_to_hard}{Schwarzschild,
    Borgnia, Gupta, Bansal, et al., 2021}) and can be configured to be
    similar to the outputs of Németh
    (\protect\hyperlink{ref-gh_Nemeth_2019}{2019})
  \item
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze.as_ascii}{\texttt{as\_ascii()}}
    provides a format similar to
    (\protect\hyperlink{ref-gh-oppenheimj2018maze}{Oppenheim, 2018};
    \protect\hyperlink{ref-eval-gpt-visual}{Singla, 2023})
  \item
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset/plotting.html\#MazePlot}{\texttt{MazePlot}}
    provides a feature-rich plotting utility with support for multiple
    paths, heatmaps over positions, and more. This is similar to the
    outputs of (\protect\hyperlink{ref-mazegenerator-net}{Alance AB,
    2019}; \protect\hyperlink{ref-gh_Ehsan_2022}{Ehsan, 2022};
    \protect\hyperlink{ref-mathematica-maze}{Guo et al., 2011};
    \protect\hyperlink{ref-mdl-suite}{Nag, 2020})
  \end{itemize}
\item
  The text format provided by
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDataset.as_tokens}{\texttt{SolvedMaze(...).as\_tokens()}}
  is similar to that of (\protect\hyperlink{ref-eval-LLM-graphs}{Liu \&
  Wu, 2023}) but with many more options, detailed
  \hyperref[sec:tokenized-output-formats]{section: \textit{\nameref{sec:tokenized-output-formats}}}.
\item
  Preserving metadata about the generation algorithm with the dataset
  itself is essential for studying the effects of distributional shifts.
  Our package efficiently stores the dataset along with its metadata in
  a single human-readable file (\protect\hyperlink{ref-zanj}{M.
  Ivanitskiy, n.d.}). As far as we are aware, no existing packages do
  this reliably.
\item
  Storing mazes as images or adjacency matrices is not only difficult to
  work with, but also inefficient. We use a highly efficient method
  detailed in
  \hyperref[sec:implementation]{section: \textit{\nameref{sec:implementation}}}.
\item
  Our package is easily installable with source code freely available.
  It is extensively tested, type hinted, benchmarked, and documented.
  Many other maze generation packages lack this level of rigor and
  scope, and some (\protect\hyperlink{ref-ayaz2008maze}{Ayaz et al.,
  2008}) appear to simply no longer be accessible.
\end{itemize}

@@

We direct readers to our
\href{https://understanding-search.github.io/maze-dataset/examples/maze_examples.html}{examples},
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html}{docs},
and
\href{https://understanding-search.github.io/maze-dataset/notebooks/}{notebooks}
for more information.

\hypertarget{generation}{%
\subsection{Generation and Basic Usage}\label{generation}}

Our package can be installed from
\href{https://pypi.org/project/maze-dataset/}{PyPi} via
\texttt{pip\ install\ maze-dataset}, or directly from the
\href{https://github.com/understanding-search/maze-dataset}{git
repository} (\protect\hyperlink{ref-maze-dataset-github}{Michael I.
Ivanitskiy et al., 2023a}).

To create a dataset, we first create a
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDatasetConfig}{\texttt{MazeDatasetConfig}}
configuration object, which specifies the seed, number, and size of
mazes, as well as the generation algorithm and its corresponding
parameters. This object is passed to a
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDataset}{\texttt{MazeDataset}}
class to create a dataset. Crucially, this
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDataset}{\texttt{MazeDataset}}
mimics the interface of a PyTorch
(\protect\hyperlink{ref-pytorch}{Paszke et al., 2019})
\href{https://pytorch.org/docs/stable/data.html}{\texttt{Dataset}}, and
can thus be easily incorporated into existing data pre-processing and
training pipelines, e.g., through the use of a \texttt{DataLoader}
class.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ maze\_dataset }\ImportTok{import}\NormalTok{ (}
\NormalTok{  MazeDataset, MazeDatasetConfig, LatticeMazeGenerators}
\NormalTok{)}
\CommentTok{\# create a config}
\NormalTok{cfg: MazeDatasetConfig }\OperatorTok{=}\NormalTok{ MazeDatasetConfig(}
\NormalTok{    name}\OperatorTok{=}\StringTok{"example"}\NormalTok{, }\CommentTok{\# names need not be unique}
\NormalTok{    grid\_n}\OperatorTok{=}\DecValTok{3}\NormalTok{,   }\CommentTok{\# size of the maze}
\NormalTok{    n\_mazes}\OperatorTok{=}\DecValTok{32}\NormalTok{, }\CommentTok{\# number of mazes in the dataset}
\NormalTok{    maze\_ctor}\OperatorTok{=}\NormalTok{LatticeMazeGenerators.gen\_dfs, }\CommentTok{\# many algorithms available}
    \CommentTok{\# (optional) algorithm{-}specific parameters}
\NormalTok{    maze\_ctor\_kwargs}\OperatorTok{=}\NormalTok{\{}\StringTok{"do\_forks"}\NormalTok{: }\VariableTok{True}\NormalTok{, ...\}, }
    \CommentTok{\# (optional) many options for restricting start/end points}
\NormalTok{    endpoint\_kwargs}\OperatorTok{=}\NormalTok{\{}\StringTok{"deadend\_start"}\NormalTok{: }\VariableTok{True}\NormalTok{, ...\},}
\NormalTok{)}
\CommentTok{\# create a dataset}
\NormalTok{dataset: MazeDataset }\OperatorTok{=}\NormalTok{ MazeDataset.from\_config(}
\NormalTok{  cfg, }\CommentTok{\# pass the config}
\NormalTok{  ..., }\CommentTok{\# other options for disk loading, parallelization, etc.}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

When initializing a dataset, options which do not affect the mazes
themselves can be specified through the
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDataset.from_config}{\texttt{from\_config()}}
factory method as necessary. These options allow for saving/loading
existing datasets instead of re-generating, parallelization options for
generation, and more. Available maze generation algorithms are static
methods of the
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMazeGenerators}{\texttt{LatticeMazeGenerators}}
namespace class and include generation algorithms based on randomized
depth-first search, Wilson's algorithm
(\protect\hyperlink{ref-wilson}{Wilson, 1996}), percolation
(\protect\hyperlink{ref-percolation}{Duminil-Copin, 2017};
\protect\hyperlink{ref-percolation-clustersize}{Fisher \& Essam, 2004}),
Kruskal's algorithm
(\protect\hyperlink{ref-kruskal1956shortest}{Kruskal, 1956}), and
others.

Furthermore, a dataset of mazes can be filtered to satisfy certain
properties. Custom filters can be specified, and some filters are
included in
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/filters.html\#MazeDatasetFilters}{\texttt{MazeDatasetFilters}}.
For example, we can require a minimum path length of three steps from
the origin to the target:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dataset\_filtered: MazeDataset }\OperatorTok{=}\NormalTok{ dataset.filter\_by.path\_length(min\_length}\OperatorTok{=}\DecValTok{3}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

All implemented maze generation algorithms are stochastic by nature. For
reproducibility, the \texttt{seed} parameter of
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDatasetConfig}{\texttt{MazeDatasetConfig}}
may be set. In practice, using provided deduplication filters, we find
that exact duplicate mazes are generated very infrequently, even when
generating very large datasets.

For use cases where mazes of different sizes, generation algorithms, or
other parameter variations are required, we provide the
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/collected_dataset.html\#MazeDatasetCollection}{\texttt{MazeDatasetCollection}}
class, which allows for creating a single iterable dataset from multiple
independent configurations.

@@

Each
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/tokenization.html\#MazeTokenizerModular}{\texttt{MazeTokenizerModular}}
is constructed from a set of several
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/tokenization.html#_TokenizerElement}{\texttt{\_TokenizerElement}}
objects, each of which specifies how different token regions or other
elements of the stringification are produced.

\input{figures/tex/fig5_mmt.tex}

@@

We provide approximate benchmarks for relative generation time across
various algorithms, parameter choices, maze sizes, and dataset sizes in
\autoref{tab:benchmarks} and \autoref{fig:benchmarks}. Experiments were
performed on a
\href{https://docs.github.com/en/actions/using-github-hosted-runners/using-github-hosted-runners/about-github-hosted-runners#standard-github-hosted-runners-for-public-repositories}{standard GitHub runner}
without parallelism.

@@

In order to replicate the exact dataset distribution of
(\protect\hyperlink{ref-easy_to_hard}{Schwarzschild, Borgnia, Gupta,
Bansal, et al., 2021}), the parameter
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/maze_dataset_config.html\#MazeDatasetConfig.endpoint_kwargs}{\texttt{MazeDatasetConfig.endpoint\_kwargs:}}
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/maze_dataset_config.html\#EndpointKwargsType}{\texttt{EndpointKwargsType}}
allows for additional constraints, such as enforcing that the start or
end point be in a ``dead end'' with only one accessible neighbor cell.
However, combining these constraints with cyclic mazes\footnote{Such as
  those generated with percolation, as was required for the work in
  (\protect\hyperlink{ref-knutson2024logicalextrapolation}{Knutson et
  al., 2024}).} can lead to an absence of valid start and end points. To
deal with this, our package provides a way to estimate the success rate
of a given configuration using a symbolic regression model trained with
PySR (\protect\hyperlink{ref-pysr}{Cranmer, 2023}). More details on this
can be found in
\href{https://understanding-search.github.io/maze-dataset/notebooks/estimate_dataset_fractions.html}{\texttt{estimate\_dataset\_fractions.ipynb}}.

@@

We describe mazes with the following representation: for a
\(2\)-dimensional lattice with \(r\) rows and \(c\) columns, we
initialize a boolean array \[
  A = \{0, 1\}^{2 \times r \times c}
\] which we refer to in the code as a
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze.connection_list}{\texttt{connection\_list}}.
The value at \(A[0,i,j]\) determines whether a \emph{downward}
connection exists from node \([i,j]\) to \([i+1, j]\). Likewise, the
value at \(A[1,i,j]\) determines whether a \emph{rightward} connection
to \([i, j+1]\) exists. Thus, we avoid duplication of data about the
existence of connections and facilitate fast lookup time, at the cost of
requiring additional care with indexing.

@@

\leavevmode\vadjust pre{\hypertarget{ref-pysr}{}}%
Cranmer, M. (2023). Interpretable machine learning for science with PySR
and SymbolicRegression. jl. \emph{arXiv Preprint arXiv:2305.01582}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-percolation}{}}%
Duminil-Copin, H. (2017). \emph{Sixty years of percolation} (No.
arXiv:1712.04651). {arXiv}. \url{http://arxiv.org/abs/1712.04651}

@@

\leavevmode\vadjust pre{\hypertarget{ref-percolation-clustersize}{}}%
Fisher, M. E., \& Essam, J. W. (2004). Some {Cluster Size} and
{Percolation Problems}. \emph{Journal of Mathematical Physics},
\emph{2}(4), 609--619. \url{https://doi.org/10.1063/1.1703745}

@@

\leavevmode\vadjust pre{\hypertarget{ref-kruskal1956shortest}{}}%
Kruskal, J. B. (1956). On the shortest spanning subtree of a graph and
the traveling salesman problem. \emph{Proceedings of the American
Mathematical Society}, \emph{7}(1), 48--50.

@@

\leavevmode\vadjust pre{\hypertarget{ref-pytorch}{}}%
Paszke, A., Gross, S., Massa, F., Lerer, A., Bradbury, J., Chanan, G.,
Killeen, T., Lin, Z., Gimelshein, N., Antiga, L., Desmaison, A., Kopf,
A., Yang, E., DeVito, Z., Raison, M., Tejani, A., Chilamkurthy, S.,
Steiner, B., Fang, L., \ldots{} Chintala, S. (2019). {PyTorch: An
Imperative Style, High-Performance Deep Learning Library}. In H.
Wallach, H. Larochelle, A. Beygelzimer, F. d'Alché-Buc, E. Fox, \& R.
Garnett (Eds.), \emph{Advances in neural information processing systems
32} (pp. 8024--8035). Curran Associates, Inc.
\url{http://papers.neurips.cc/paper/9015-pytorch-an-imperative-style-high-performance-deep-learning-library.pdf}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wilson}{}}%
Wilson, D. B. (1996). Generating random spanning trees more quickly than
the cover time. \emph{Proceedings of the Twenty-Eighth Annual {ACM}
Symposium on {Theory} of Computing - {STOC} '96}, 296--303.
\url{https://doi.org/10.1145/237814.237880}

>>>>

\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\urlstyle{same}  % don't use monospace font for urls
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{american}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}

\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\input{preamble.tex}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

  \begin{itemize}
  \tightlist
  \item
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/rasterized.html\#RasterizedMazeDataset}{\texttt{RasterizedMazeDataset}},
    utilizing
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze.as_pixels}{\texttt{as\_pixels()}},
    which can exactly mimic the outputs provided in
    \texttt{easy-to-hard-data}(\protect\hyperlink{ref-easy_to_hard}{Schwarzschild,
    Borgnia, Gupta, Bansal, et al., 2021}) and can be configured to be
    similar to the outputs of Németh
    (\protect\hyperlink{ref-gh_Nemeth_2019}{2019})
  \item
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze.as_ascii}{\texttt{as\_ascii()}}
    provides a format similar to
    (\protect\hyperlink{ref-gh-oppenheimj2018maze}{Oppenheim, 2018};
    \protect\hyperlink{ref-eval-gpt-visual}{Singla, 2023})
  \item
    \href{https://understanding-search.github.io/maze-dataset/maze_dataset/plotting.html\#MazePlot}{\texttt{MazePlot}}
    provides a feature-rich plotting utility with support for multiple
    paths, heatmaps over positions, and more. This is similar to the
    outputs of (\protect\hyperlink{ref-mazegenerator-net}{Alance AB,
    2019}; \protect\hyperlink{ref-gh_Ehsan_2022}{Ehsan, 2022};
    \protect\hyperlink{ref-mathematica-maze}{Guo et al., 2011};
    \protect\hyperlink{ref-mdl-suite}{Nag, 2020})
  \end{itemize}
\item
  The text format provided by
  \href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDataset.as_tokens}{\texttt{SolvedMaze(...).as\_tokens()}}
  is similar to that of (\protect\hyperlink{ref-eval-LLM-graphs}{Liu \&
  Wu, 2023}) but with many more options, detailed
  \secref{sec:tokenized-output-formats}.
\item
  Preserving metadata about the generation algorithm with the dataset
  itself is essential for studying the effects of distributional shifts.
  Our package efficiently stores the dataset along with its metadata in
  a single human-readable file (\protect\hyperlink{ref-zanj}{M.
  Ivanitskiy, n.d.}). As far as we are aware, no existing packages do
  this reliably.
\item
  Storing mazes as images or adjacency matrices is not only difficult to
  work with, but also inefficient. We use a highly efficient method
  detailed in \secref{sec:implementation}.
\item
  Our package is easily installable with source code freely available.
  It is extensively tested, type hinted, benchmarked, and documented.
  Many other maze generation packages lack this level of rigor and
  scope, and some (\protect\hyperlink{ref-ayaz2008maze}{Ayaz et al.,
  2008}) appear to simply no longer be accessible.
\end{itemize}

@@

We direct readers to our
\href{https://understanding-search.github.io/maze-dataset/examples/maze_examples.html}{examples},
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html}{docs},
and
\href{https://understanding-search.github.io/maze-dataset/notebooks/}{notebooks}
for more information. Our package can be installed from
\href{https://pypi.org/project/maze-dataset/}{PyPi} via
\texttt{pip\ install\ maze-dataset}, or directly from the
\href{https://github.com/understanding-search/maze-dataset}{git
repository} (\protect\hyperlink{ref-maze-dataset-github}{Michael I.
Ivanitskiy et al., 2023a}).

Datasets of mazes are created from a
\docslinkcodemain{MazeDatasetConfig} configuration object, which allows
specifying the number of mazes, their size, the generation algorithm,
and various parameters for the generation algorithm. Datasets can also
be filtered after generation to satisfy certain properties. Custom
filters can be specified, and some filters are included in
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/dataset/filters.html\#MazeDatasetFilters}{\texttt{MazeDatasetFilters}}

@@

@@

We benchmarks for generation time across various configurations in
\autoref{tab:benchmarks} and \autoref{fig:benchmarks}. Experiments were
performed on a
\href{https://docs.github.com/en/actions/using-github-hosted-runners/using-github-hosted-runners/about-github-hosted-runners\#standard-github-hosted-runners-for-public-repositories}{standard
GitHub runner} without parallelism.

@@

Maze generation under certain constraints may not always be successful,
and for this we provide a way to estimate the success rate of a given
configuration, described in \autoref{fig:sre}.

@@

\input{figures/tex/fig8_impl.tex}

@@

@@

@@

@@

@@

@@
